\Huge \bf \sc Calibration of an inertial measurement unit

### 2013-07-16 latex/paper_sensores/paper.tex
paper sensores, pequenias correcciones

Let $\boldsymbol{\theta}_s$ (where the subindex $s$ refers to a sensor) be the parameter vector of a certain sensor. We can define this vector as:
\begin{equation}
\boldsymbol{\theta} = [k_{sx},k_{sy},k_{sy},b_{sx},b_{sy},b_{sy}, \alpha_{sxy},\alpha_{sxz},\alpha_{syx},\alpha_{syz},\alpha_{szx},\alpha_{szy}]^T
\label{eq:theta}
\end{equation}

In equation \ref{eq:theta}, $k_{si}$, with $i=1,2,3$ are the diagonal elements of the matrix $\mathbf{K}_s$, $b_{si}$, with $i = 1,2,3$ are the elements of vector $\mathbf{b}_s$ and $\alpha_{sij}$, with $i = 1,2,3$, $j = 1,2,3$ and $i \neq j$ are the elements outside the diagonal of the matrix $\mathbf{T}_s^p$.\\

As adjust criterium we choose to minimize the sum of the squares of the norms of the diferences between true accleracion and measured acceleration. This problem can be written as follows:

@@

In equation \ref{eq:calib_problem}, $M$ is the cardinal of the training set, $\mathbf{s}_i^p$ is the true magnitude (acceleration or angular speed) and $\tilde{\mathbf{s}}_i$ are the values given by the sensor.\\

@@

\begin{itemize}
\item The typical sensitivity for each axis is $256 bits/g \approx 26.10 m^{s-2}$.
\item The typical offset for each axis is $0 ms^{-2}$.
\item As the axis should be as orthogonal as posible is reasonable to think that the rotation angles $\alpha_{aij}$ are near zero. 
\end{itemize}

@@

As we did for the accelerometer, we are going to choose a seed based on the information in the device's datacheet \cite{bib:gyro_data}:

>>>>

Let $\boldsymbol{\theta}_s$ (where the subindex $s$ refers to a sensor) be the parameter vector of a certain sensor. We can define this vector as:
\begin{equation}
\boldsymbol{\theta} = [k_{sx},k_{sy},k_{sz},b_{sx},b_{sy},b_{sz}, \alpha_{sxy},\alpha_{sxz},\alpha_{syx},\alpha_{syz},\alpha_{szx},\alpha_{szy}]^T
\label{eq:theta}
\end{equation}

In equation \ref{eq:theta}, $k_{si}$, with $i=\{x, y, z\}$ are the diagonal elements of the matrix $\mathbf{K}_s$, $b_{si}$, with $i=\{x, y, z\}$ are the elements of vector $\mathbf{b}_s$ and $\alpha_{sij}$, with $i=\{x, y, z\}$, $j=\{x, y, z\}$ and $i \neq j$ are the elements outside the diagonal of the matrix $\mathbf{T}_s^p$.\\

As adjust criterion we choose to minimize the sum of the squares of the norms of the diferences between true acceleration (or angular speed) and measured acceleration (or angular speed). This problem can be written as follows:

@@

In equation \ref{eq:calib_problem}, $M$ is the cardinal of the training set, $\mathbf{s}_i^p$ is the true magnitude (acceleration or angular speed) and $\tilde{\mathbf{s}}_i$ are the values given by the sensor. This problem can be solved with \emph{MatLab} function \emph{lsqnonlin}.\\

@@

\begin{itemize}
\item The typical sensitivity for each axis is $256 bits/g \approx 26.10 ms^{-2}$.
\item The typical offset for each axis is $0 ms^{-2}$.
\item As the axis should be as orthogonal as posible is reasonable to think that the rotation angles $\alpha_{aij}$ are near zero. 
\end{itemize}

@@

As we did for the accelerometer, we are going to choose a seed based on the information in the device's datasheet \cite{bib:gyro_data}:
